What we {\sf eval} in the shadows

### 2021-04-01 paper/main.tex
Better description of the possible envir types

The environment argument can be \c{NULL}, a \c{List} or a data frame. This
happens in 3.5\% of the cases: \eval copies the fields of the list or data frame
and creates bindings for them in a new environment. This pattern is used to
evaluate formulas which can directly refer to the fields of the data. The
\c{envir} argument can also be a number $n$. It means that the environment in
which the expressions is evaluated will be the result of \c{sys.call(n)} where
$n$ refers to the $n$-th stack frame.

@@

We observe that a disproportionately high number of core R \eval calls access
the caller's environment. This is because many core R functions call functions
that pass the result of \c{parent.frame()} to an \eval. A disproportionately
high number of calls to \eval happens in an extended top-level environment. This
can be explained by the fact that many packages evaluate code passed from the
user's workspace in the top-level environment to access the bindings.

@@

\paragraph{Package environments.} Another kind of environments that is passed to \eval is the environment of a package. 
 It refers to the \emph{namespace} of a package. A call to
 \c{library(packageName)}, which load libraries in R, for instance, will populate
 environment \c{package:packageName}. It is a \emph{base} function though, so we
 do not see it in the CRAN dataset. However, R still makes it possible to access
 any package environments and \packageNbPackageEnvSites call sites, \ie
 \packagePackageEnvSitePercent access a package environment, from
 \packageNbPackageEnvPackages different packages. Those packages perform
 introspection, to represent and search any environment by name, in package
 \emph{envnames}, to containerize tests, as with \emph{testthat} and
 \emph{unitizer}, to create a custom OOP system with \emph{R.oo}, or to create
 poor man's hidden functions in \emph{USSCXenaTools}.

@@

>>>>

The \c{envir} argument of \eval can be an actual environment, but also \c{Null}, a list, a dataframe, a pairlist or even an integer. % Sometimes also a double, but it is cast to integer anyway.

Most of the time, \ie in \packageEnvirEnvSitePercent of the sites, \eval is passed an actual environment. In \packageNbEnvirIncorrectSites sites (\packageEnvirIncorrectSitePercent), \eval is passed an incorrect argument, for instance \c{NA}, a boolean, which makes \eval fail.

\c{NULL}, a \c{list} or a data frame, or an integer, happen in \packageEnvirUnusualSitePercent of the cases: \eval copies the fields of the list or data frame
and creates bindings for them in a new environment. This pattern is used to
evaluate formulas which can directly refer to the fields of the data. The
\c{envir} argument can also be a number $n$. It means that the environment in
which the expressions is evaluated will be the result of \c{sys.call(n)} where
$n$ refers to the $n$-th stack frame.

@@

We observe that a disproportionately high number of core R \eval calls access
the caller's environment. This is because many R functions call functions
that pass the result of \c{parent.frame()} to an \eval. A disproportionately
high number of calls to \eval happens in an extended top-level environment. This
can be explained by the fact that many packages evaluate code passed from the
user's workspace in the top-level environment to access the bindings.

@@

\paragraph{Package environments.} Another kind of environments that is passed to \eval is the environment of a package. 
 It refers to the \emph{namespace} of a package. A call to
 \c{library(packageName)}, which loads libraries in R, for instance, will populate
 environment \c{package:packageName}. It is a \emph{base} function though, so we
 do not see it in the CRAN dataset. However, R still makes it possible to access
 any package environments and \packageNbPackageEnvSites call sites, \ie
 \packagePackageEnvSitePercent access a package environment, from
 \packageNbPackageEnvPackages different packages. Those packages perform
 introspection, to represent and search any environment by name, in package
 \emph{envnames}, to containerize tests, as with \emph{testthat} and
 \emph{unitizer}, to create a custom OOP system with \emph{R.oo}, or to create
 poor man's hidden functions in \emph{USSCXenaTools}.

@@

\paragraph{\c{enclos} argument.}
